---
title: "Benthotorch validation with Type II regression model & pettitt tests"
author: "Bella Oleksy"
date: "07/02/2018"
output: html_document
fig_width: 6
fig_height: 2.5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=6, fig.height=6) 
```

# Data loading
Loaded data and condensed mondo file into something managable for this analysis. 

```{r loading data, warning=FALSE, message=FALSE, tidy=TRUE }

benthotorch_validation_raw <- read.csv("data/MassCalcs_20180604.csv")

library(dplyr) # for tidy data!
library(skimr) # for skim() function
library(knitr) # to print table in R markdown
library(ggplot2) # for plots
library(kableExtra) # for making tables pretty/legible
library(lmodel2) # for type II regression model
library(scales) # to add percentages to plots and pretty_breaks()
glimpse(benthotorch_validation_raw)

benthotorch_validation_short <- benthotorch_validation_raw %>%
  select(run_ID,pigment_ID, area, bentho_green,bentho_green_percent,
         bentho_diatom,bentho_diatom_percent,bentho_cyano,bentho_cyano_percent,
         bentho_totalchla, mass_ug_cm2, perc_green_UPLC,
         perc_diat_UPLC, perc_cyano_candidate, investigator) # select only the variables of interest

skim_object1 <- skim(benthotorch_validation_short) %>%
  filter(stat=="hist") #create skim table

benthotorch_validation_short$investigator <- factor(benthotorch_validation_short$investigator, levels=c('Chris','Bella','Whit',
                                               'Tristan'))

```

# Summary of data

```{r subset, results="hide" , fig.width=8}
#Fuco data subset
data_fuco <- benthotorch_validation_short %>%
  filter(pigment_ID=="fuco") %>%
  filter(mass_ug_cm2 < 1) %>% # extreme removing outliers
  mutate(log_UPLC_diat = log10(mass_ug_cm2 + .01),
         log_UPLC_diat_perc = log10(perc_diat_UPLC + .01),
         log_BT_diat = log10(bentho_diatom + .01),
         log_BT_diat_perc = log10(bentho_diatom_percent + 0.01)) %>%
  select(run_ID, pigment_ID,log_UPLC_diat, log_UPLC_diat_perc, perc_diat_UPLC,bentho_diatom_percent, log_BT_diat, log_BT_diat_perc, investigator)



benthotorch_validation_short %>%
  filter(pigment_ID=="fuco") %>%
  select(bentho_diatom_percent)


#Chl a total data subset
data_chla_total <- benthotorch_validation_short %>%
  filter(pigment_ID=="chla_total") %>%
  mutate(log_UPLC_chla = log10(mass_ug_cm2 + 0.01),
         log_BT_chla = log10(bentho_totalchla + 0.01))

#Green subset
data_chlb_total <- benthotorch_validation_short %>%
  filter(pigment_ID=="chlb_total") %>%
  filter(mass_ug_cm2 < 0.15) %>% #removing extreme outliers
  mutate(sqrt_BT_green = sqrt(bentho_green),
         sqrt_UPLC_chlb = sqrt(mass_ug_cm2),
         sqrt_BT_green_perc = sqrt(bentho_green_percent),
         sqrt_UPLC_chlb_perc = sqrt(perc_green_UPLC)) %>%
  select(run_ID, pigment_ID, mass_ug_cm2, sqrt_BT_green, sqrt_UPLC_chlb, sqrt_BT_green_perc,  perc_green_UPLC, sqrt_UPLC_chlb_perc, bentho_green_percent,investigator)


#Cyano subset all
data_myxo_full <- benthotorch_validation_short %>%
  filter(pigment_ID=="myxo") %>%
  filter(mass_ug_cm2 < 0.15) %>% # removing extreme high outliers
  mutate(sqrt_BT_cyano = sqrt(bentho_cyano),
         sqrt_BT_cyano_perc = sqrt(bentho_cyano_percent),
         sqrt_UPLC_myxo = sqrt(mass_ug_cm2),
         sqrt_UPLC_myxo_perc = sqrt(perc_cyano_candidate)) %>%
  select(run_ID, pigment_ID, sqrt_BT_cyano, sqrt_BT_cyano_perc, sqrt_UPLC_myxo, sqrt_UPLC_myxo_perc, investigator)


#Cyano subset - nonzero BT values
data_myxo_nonzeros <- benthotorch_validation_short %>%
  filter(pigment_ID=="myxo") %>%
  filter(mass_ug_cm2 < 0.15) %>% # removing extreme outliers
  filter(mass_ug_cm2 > 0) %>%
  mutate(sqrt_BT_cyano = sqrt(bentho_cyano),
         sqrt_BT_cyano_perc = sqrt(bentho_cyano_percent),
         sqrt_UPLC_myxo = sqrt(mass_ug_cm2),
         sqrt_UPLC_myxo_perc = sqrt(perc_cyano_candidate)) %>%
  select(run_ID, pigment_ID, sqrt_BT_cyano, sqrt_BT_cyano_perc, sqrt_UPLC_myxo, sqrt_UPLC_myxo_perc)
```


# Plot figures for MS 

####Greens (perc of total and mass to mass)
```{r green plots, include=FALSE, tidy=TRUE, fig.dim = c(6, 6)}
library(ggplot2)
library(ggthemes)
library(ggpmisc)

#Customize theme 
#http://joeystanley.com/blog/custom-themes-in-ggplot2 
theme_BT <- function () { 
    theme_base(base_size=15, base_family="Helvetica") %+replace% 
        theme(
            panel.background  = element_blank(),
            plot.background = element_rect(fill="white", colour=NA), 
            legend.background = element_rect(fill="transparent", colour=NA),
            legend.key = element_rect(fill="transparent", colour=NA)
            
        )
}
theme_set(theme_BT())  # pre-set the bw theme

investigator_colors <- c("#ff0000", "#0000ff", "#00ff00", "#ff00bf") #treatment colors



#Source for annotating plot with equation:
# https://stackoverflow.com/questions/7549694/adding-regression-line-equation-and-r2-on-graph


glimpse(data_chlb_total)
green_lm1_eqn <- data_chlb_total$sqrt_BT_green_perc ~ data_chlb_total$sqrt_UPLC_chlb_perc 
green_lm2_eqn <- data_chlb_total$sqrt_BT_green ~ data_chlb_total$sqrt_UPLC_chlb
green_low_eqn <- Chlb_total_low$sqrt_BT_green_perc ~ Chlb_total_low$sqrt_UPLC_chlb_perc 
green_high_eqn <- Chlb_total_high$sqrt_BT_green_perc ~ Chlb_total_high$sqrt_UPLC_chlb_perc 
green_nonzero_eqn_1 <- data_chlb_total_nonzeros$sqrt_BT_green_perc ~ data_chlb_total_nonzeros$sqrt_UPLC_chlb_perc
green_nonzero_eqn_2 <- data_chlb_total_nonzeros$sqrt_BT_green ~ data_chlb_total_nonzeros$sqrt_UPLC_chlb


green1 <- ggplot(data_chlb_total, aes(y=sqrt_BT_green_perc,x=sqrt_UPLC_chlb_perc)) +
  geom_point(size=3, alpha = 0.3,  position = position_jitter())+
   stat_poly_eq(formula = green_lm1_eqn, 
                label.x.npc="right", label.y.npc="top", aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")), 
                parse = TRUE) +
     ggtitle("Green algae")+
    expand_limits(y=c(0,1.0),x=c(0,0.8))+
  scale_y_continuous(breaks=pretty_breaks(), name = expression("sqrt"~rel.~abund.~green["BT"]~"")) +
  scale_x_continuous(breaks=pretty_breaks(), name = expression("sqrt"~rel.~abund.~chl~italic("b")["UPLC"]~""))



green2 <- ggplot(data_chlb_total, aes(y=sqrt_BT_green,x=sqrt_UPLC_chlb)) +
  geom_point(size=3, alpha = 0.3,  position = position_jitter())+
   geom_smooth(method = "lm", se=FALSE, color="black") +
   stat_poly_eq(formula = green_lm2_eqn, 
                label.x.npc="right", label.y.npc="top", aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")), 
                parse = TRUE) +
      ggtitle("Green algae")+
    expand_limits(y=1.0,x=0.4)+
  scale_y_continuous(breaks=pretty_breaks(n=5), name = expression("sqrt"~green["BT"]~(mu*g/cm^2))) +
  scale_x_continuous(breaks=pretty_breaks(n=5), name = expression("sqrt"~chlb["UPLC"]~(mu*g/cm^2)))
green2

#Changepoint figure for % green vs % chlb
Chlb_total_low=subset(data_chlb_total, sqrt_UPLC_chlb_perc<0.115)
Chlb_total_high=subset(data_chlb_total, sqrt_UPLC_chlb_perc>0.115)

ChlbMod=lm(sqrt_BT_green_perc~sqrt_UPLC_chlb_perc, data=data_chlb_total)
ChlbMod_low=lm(sqrt_BT_green_perc~sqrt_UPLC_chlb_perc, data=Chlb_total_low)
summary(ChlbMod_low)
#Intercept =  -0.00825, slope = 0.06835
ChlbMod_high=lm(sqrt_BT_green_perc~sqrt_UPLC_chlb_perc, data=Chlb_total_high)
summary(ChlbMod_high)
#Interecept = 0.5597, slope = -0.3722


breaks = function(x) unique(floor(pretty(seq(0, (max(x) + 1) * 1.1))))


green_low <- ggplot(Chlb_total_low, aes(y=sqrt_BT_green_perc,x=sqrt_UPLC_chlb_perc)) +
   geom_point(size=3, alpha = 0.3,  position = position_jitter())+
   geom_smooth(method = "lm", se=FALSE, color="black") +
   stat_poly_eq(formula = green_low_eqn, 
                label.x.npc="right", label.y.npc="top", aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")), 
                parse = TRUE) +
     ggtitle("Green algae (below breakpoint)")+
  expand_limits(y=c(0,1.0),x=c(0,0.12))+
  scale_y_continuous(breaks=pretty_breaks(), name = expression("sqrt"~rel.~abund.~green["BT"]~"")) +
  scale_x_continuous(breaks=pretty_breaks(), name = expression("sqrt"~rel.~abund.~chl~italic("b")["UPLC"]~""))

  # scale_y_continuous(breaks=pretty_breaks(), labels= scales::percent, name = expression("SR"~green["BT"]~"")) +
  # scale_x_continuous(breaks=c(0,0.02,.04,.06,.08,0.10,.12), labels=c("0%","2%", "4%", "6%","8%","10%", "12%"),  name = expression("SR"~chlb["UPLC"]~""))



green_high <- ggplot(Chlb_total_high, aes(y=sqrt_BT_green_perc,x=sqrt_UPLC_chlb_perc)) +
  geom_point(size=3, alpha = 0.3,  position = position_jitter())+
   geom_smooth(method = "lm", se=FALSE, color="black") +
   stat_poly_eq(formula = green_high_eqn, 
                label.x.npc="right", label.y.npc="top", aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")), 
                parse = TRUE) +
     ggtitle("Green algae (above breakpoint)")+
  expand_limits(y=c(0,1.0),x=c(0,0.8))+
  scale_y_continuous(breaks=pretty_breaks(), name = expression("sqrt"~rel.~abund.~green["BT"]~"")) +
  scale_x_continuous(breaks=pretty_breaks(), name = expression("sqrt"~rel.~abund.~chl~italic("b")["UPLC"]~""))


  # scale_y_continuous(breaks=seq(0, 1.0, 0.2), labels= scales::percent, name = expression("SR"~green["BT"]~"")) +
  # scale_x_continuous(breaks=c(0,0.2,0.4,0.6,0.8), labels=c("0%","20%", "40%", "60%","80%"), name = expression("SR"~chlb["UPLC"]~""))



#What if we exclude the zero values for Chlb(UPLC), where we detected 
#green algae but the BT didn't.
data_chlb_total_nonzeros <- data_chlb_total %>%
  filter(sqrt_BT_green > 0)
nonzero_chlb_lm <- lm(sqrt_BT_green~sqrt_UPLC_chlb, data=data_chlb_total_nonzeros)
summary(nonzero_chlb_lm)
nonzero_chlb_perc_lm <- lm(sqrt_BT_green_perc~sqrt_UPLC_chlb_perc, data=data_chlb_total_nonzeros)
summary(nonzero_chlb_perc_lm)

green_nonzero2 <- ggplot(data_chlb_total_nonzeros, aes(y=sqrt_BT_green,x=sqrt_UPLC_chlb)) +
  geom_point(size=3, alpha = 0.3,  position = position_jitter())+
   geom_smooth(method = "lm", se=FALSE, color="black") +
   stat_poly_eq(formula = green_nonzero_eqn_2, 
                label.x.npc="right", label.y.npc="top", aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")), 
                parse = TRUE) +
     ggtitle("Green algae (non-zeros)")+
  scale_y_continuous(name = expression("sqrt"~green["BT"]~(mu*g/cm^2))) +
  scale_x_continuous(name = expression("sqrt"~chlb["UPLC"]~(mu*g/cm^2)))


green_nonzero1 <- ggplot(data_chlb_total_nonzeros, aes(y=sqrt_BT_green_perc,x=sqrt_UPLC_chlb_perc)) +
  geom_point(size=3, alpha = 0.3,  position = position_jitter())+
   geom_smooth(method = "lm", se=FALSE, color="black") +
   stat_poly_eq(formula = green_nonzero_eqn_1, 
                label.x.npc="right", label.y.npc="top", aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")), 
                parse = TRUE) +
     ggtitle("Green algae (non-zeros)")+
  scale_y_continuous(breaks=pretty_breaks(),name = expression("sqrt"~rel.~abund.~green["BT"]~"")) +
  scale_x_continuous(breaks=pretty_breaks(),name = expression("sqrt"~rel.~abund.~chl~italic("b")["UPLC"]~""))


```

```{r, echo=FALSE}
green1
green2
green_low
green_high
green_nonzero1
green_nonzero2
```

####Cyano (perc of total and mass to mass)

```{r cyano plots, include=FALSE, tidy=TRUE, fig.dim = c(6, 6)}


glimpse(data_myxo_full)
cyano_lm1_eqn <-  data_myxo_full$sqrt_BT_cyano_perc~data_myxo_full$sqrt_UPLC_myxo_perc 
cyano_lm2_eqn <-   data_myxo_full$sqrt_BT_cyano~data_myxo_full$sqrt_UPLC_myxo


cyano1 <- ggplot(data_myxo_full, aes(y=sqrt_BT_cyano_perc,x=sqrt_UPLC_myxo_perc)) +
  geom_point(size=3, alpha = 0.3,  position = position_jitter())+
   # geom_smooth(method = "lm", se=FALSE, color="black") +
   stat_poly_eq(formula = cyano_lm1_eqn, 
                label.x.npc="right", label.y.npc="top", aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")), 
                parse = TRUE) +
  ggtitle("Cyanobacteria")+
  expand_limits(y=1.0,x=0.4)+
  scale_y_continuous(breaks=pretty_breaks(), name = expression("sqrt"~rel.~abund.~cyano["BT"]~"")) +
  scale_x_continuous(breaks=pretty_breaks(), name = expression("sqrt"~rel.~abund.~myxo["UPLC"]~""))




cyano2 <- ggplot(data_myxo_full, aes(y=sqrt_BT_cyano,x=sqrt_UPLC_myxo)) +
  geom_point(size=3, alpha = 0.3,  position = position_jitter())+
   geom_smooth(method = "lm", se=FALSE, color="black") +
   stat_poly_eq(formula = cyano_lm2_eqn, 
                label.x.npc="right", label.y.npc="top", aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")), 
                parse = TRUE) +
  ggtitle("Cyanobacteria")+
  expand_limits(y=0.6,x=0.3)+
  scale_y_continuous(name = expression("sqrt"~cyano["BT"]~(mu*g/cm^2))) +
  scale_x_continuous(name = expression("sqrt"~myxo["UPLC"]~(mu*g/cm^2)))


glimpse(data_myxo_nonzeros)
cyano_lm3_eqn <-  data_myxo_nonzeros$sqrt_BT_cyano_perc~data_myxo_nonzeros$sqrt_UPLC_myxo_perc
cyano_lm4_eqn <-   data_myxo_nonzeros$sqrt_BT_cyano~data_myxo_nonzeros$sqrt_UPLC_myxo

# summary(model1)
cyano3 <- ggplot(data_myxo_nonzeros, aes(y=sqrt_BT_cyano_perc,x=sqrt_UPLC_myxo_perc)) +
  geom_point(size=3, alpha = 0.3,  position = position_jitter())+
   stat_poly_eq(formula = cyano_lm3_eqn,
                label.x.npc="right", label.y.npc="top", aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
                parse = TRUE) +
  ggtitle("Cyanobacteria (without zeros)")+
      expand_limits(y=c(0,1.0),x=c(0,0.4))+
  scale_y_continuous(breaks=pretty_breaks(), name = expression("sqrt"~rel.~abund.~cyano["BT"]~"")) +
  scale_x_continuous(breaks=pretty_breaks(), name = expression("sqrt"~rel.~abund.~myxo["UPLC"]~""))


cyano4 <- ggplot(data_myxo_nonzeros, aes(y=sqrt_BT_cyano,x=sqrt_UPLC_myxo)) +
  geom_point(size=3, alpha = 0.3,  position = position_jitter())+
   geom_smooth(method = "lm", se=FALSE, color="black") +
   stat_poly_eq(formula = cyano_lm4_eqn,
                label.x.npc="right", label.y.npc="top", aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
                parse = TRUE) +
  ggtitle("Cyanobacteria (without zeros)")+
    expand_limits(y=c(0,0.6),x=c(0,0.3))+
  scale_y_continuous(name = expression("sqrt"~cyano["BT"]~(mu*g/cm^2))) +
  scale_x_continuous(name = expression("sqrt"~myxo["UPLC"]~(mu*g/cm^2)))

```

```{r, echo=FALSE}
cyano1
cyano2
cyano3
cyano4
```

####Diatoms (perc of total and mass to mass)

```{r diatom plots, include=FALSE}
glimpse(data_fuco)
diat_lm1_eqn <- data_fuco$log_BT_diat_perc~data_fuco$log_UPLC_diat_perc
diat_lm2_eqn <- data_fuco$log_BT_diat~data_fuco$log_UPLC_diat


diatoms1 <- ggplot(data_fuco, aes(y=log_BT_diat_perc,x=log_UPLC_diat_perc)) +
  geom_point(size=3, alpha = 0.3,  position = position_jitter())+
   geom_smooth(method = "lm", se=FALSE, color="black") +
   stat_poly_eq(formula = diat_lm1_eqn, 
                label.x.npc="right", label.y.npc="top", aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")), 
                parse = TRUE) +
  ggtitle("Diatoms")+
  expand_limits(y=0.3,x=0.3)+
  scale_y_continuous(breaks=pretty_breaks(), name = expression("log"~rel.~abund.~diatoms["BT"]~"")) +
  scale_x_continuous(breaks=pretty_breaks(), name = expression("log"~rel.~abund.~fuco["UPLC"]~""))



diatoms2 <- ggplot(data_fuco, aes(y=log_BT_diat,x=log_UPLC_diat)) +
  geom_point(size=3, alpha = 0.3,  position = position_jitter())+

   stat_poly_eq(formula = diat_lm2_eqn, 
                label.x.npc="right", label.y.npc="top", aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")), 
                parse = TRUE) +
  ggtitle("Diatoms")+
    expand_limits(y=0.80,x=0.20)+
  scale_y_continuous(breaks=pretty_breaks(n=6),name = expression(log~diatoms["BT"]~(mu*g/cm^2))) +
  scale_x_continuous(breaks=pretty_breaks(n=6), name = expression(log~fuco["UPLC"]~(mu*g/cm^2)))

```
```{r, echo=FALSE}
diatoms1
diatoms2
```

####Total chla (mass to mass)

```{r total chla plots, include=FALSE}
glimpse(data_chla_total)
chla_lm1_eqn <- data_chla_total$log_BT_chla ~data_chla_total$log_UPLC_chla


chla1 <- ggplot(data_chla_total, aes(y=log_BT_chla,x=log_UPLC_chla)) +
  geom_point(size=3, alpha = 0.3,  position = position_jitter())+
   geom_smooth(method = "lm", se=FALSE, color="black") +
   stat_poly_eq(formula = chla_lm1_eqn, 
                label.x.npc="right", label.y.npc="top", aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")), 
                parse = TRUE) +
  ggtitle(expression(paste(bold("Total chlorophyll "), bolditalic("a"))))+
  expand_limits(x=0.8, y=0.8)+
  scale_y_continuous(name = expression(log~chl~italic("a")["BT"]~(mu*g/cm^2))) +
  scale_x_continuous(name = expression(log~chl~italic("a")["UPLC"]~(mu*g/cm^2)))

```
```{r, echo=FALSE}
chla1
```

##**MS PLOTS**
```{r all figures, echo=FALSE, include=FALSE}
library(grid) 
library(ggpubr)
library(gridExtra)


###UPDATED STACKED FIGURE FOR MANUSCRIPT (Figure 2)
chla_panel <- ggarrange(NULL,chla1,NULL,
                        ncol=3,nrow=1,
                        widths=c(0.2,0.6,0.2),
                        labels=c("","A",""))
all_stacked <- ggarrange(chla_panel,
               ggarrange(
                        green1 , green2 ,
                        diatoms1 , diatoms2 ,
                        cyano1 , cyano2 ,
                        cyano3 , cyano4,
          align="hv",
          ncol = 2, nrow = 4,
          labels = c("B", "C", "D", "E", "F", "G", "H","I")),
          nrow=2,
          widths = c(4,4), heights = c(0.3,1.0))
ggsave("figures/figure2-A_allpigments_transformation_fixed_12x16.tiff", width=12, height=16, units="in")


chla_panel <- ggarrange(NULL,chla1,NULL,
                        ncol=3,nrow=1,
                        widths=c(0.2,0.6,0.2),
                        labels=c("","A",""))
all_stacked <- ggarrange(chla_panel,
               ggarrange(
                        green1 , green2 ,
                        diatoms1 , diatoms2 ,
                        cyano1 , cyano2 ,
                        cyano3 , cyano4,
          align="hv",
          ncol = 2, nrow = 4,
          labels = c("B", "C", "D", "E", "F", "G", "H","I")),
          nrow=2,
          widths = c(4,4), heights = c(0.3,1.0))
ggsave("figures/figure2-B_allpigments_transformation_fixed_8x16.tiff", width=8, height=16,units="in")


#Breakpoint figure
breakpoint <- 
               ggarrange(green_low , green_high ,
          align="v",
          ncol = 2, nrow = 1,
          labels = c("A", "B"),
          widths = c(4,4), heights = c(0.3,0.3))
ggsave("figures/figure3_green_breakpoints_transformation_fixed.tiff", width=12, height=8,units="in")

#Non-zero green figures
green_nonzeros <-
               ggarrange(green_nonzero1 , green_nonzero2 ,
          align="v",
          ncol = 2, nrow = 1,
          labels = c("A", "B"),
          widths = c(4,4), heights = c(0.3,0.3))
ggsave("figures/figX_green_nonzeros_transformation_fixed.png", width=12, height=8,units="in")

#Non-zero green figures with regular green
green_allfigs <-
               ggarrange(green1, green2,
                         green_nonzero1 , green_nonzero2 ,
          align="v",
          ncol = 2, nrow = 2,
          labels = c("A", "B", "C","D"),
          widths = c(4,4), heights = c(0.3,0.3))
ggsave("figures/figX_green_allfigs_transformation_fixed.png", width=12, height=12,units="in")



```


# ANCOVA & mixed effects models
Output from an exploratory analysis. Starting with greens, followed by diatoms, cyanobacteria, and total chlorophylls. 

##Greens
#####ANCOVA greens + investigator (proxy for site)
```{r ANCOVA greens, echo=FALSE}
greens1_covariates <- ggplot(data_chlb_total,
  aes(y=sqrt_BT_green_perc,x=sqrt_UPLC_chlb_perc,color=investigator)) +
  geom_point(size=3, alpha = 0.6,  position = position_jitter())+
  geom_smooth(method = "lm", se=FALSE, show.legend=FALSE) +
  ggtitle("Green algae")+
  expand_limits(y=0.9,x=0.8)+
  scale_y_continuous(breaks=pretty_breaks(), name = expression("sqrt"~rel.~abund.~green["BT"]~"")) +
  scale_x_continuous(breaks=pretty_breaks(), name = expression("sqrt"~rel.~abund.~chl~italic("b")["UPLC"]~""))+
  scale_color_manual(values=investigator_colors,
                    name="Site",
                    breaks=c("Chris","Bella","Whit","Tristan"),
                    labels=c("SRL", "LV", "PR", "RMNP"))+
  theme(legend.position="none")
greens1_covariates


# greens1_covariates_untransformed <- ggplot(data_chlb_total,
#   aes(y=bentho_green_percent,x=perc_green_UPLC,color=investigator)) +
#   geom_point(size=3, alpha = 0.6,  position = position_jitter())+
#   geom_smooth(method = "lm", se=FALSE, show.legend=FALSE) +
#   ggtitle("Green algae - untransformed")+
#   expand_limits(y=0.9,x=0.8)+
#   scale_y_continuous(breaks=pretty_breaks(n=5), labels= scales::percent, name = expression("sqrt"~green["BT"]~"%")) +
#   scale_x_continuous(breaks=pretty_breaks(n=5), labels= scales::percent, name = expression("sqrt"~chlb["UPLC"]~"%")) +
#   scale_color_manual(values=investigator_colors,
#                     name="Site",
#                     breaks=c("Chris","Bella","Whit","Tristan"),
#                     labels=c("SRL", "LV", "PR", "RMNP"))+
#   theme(legend.position="none")
# greens1_covariates_untransformed
```

```{r,tidy=TRUE, collapse=TRUE}
library(car)
ANCOVA_greens1_add <- lm(sqrt_BT_green_perc ~ sqrt_UPLC_chlb_perc + investigator, data=data_chlb_total)
Anova(ANCOVA_greens1_add)

options(contrasts=c("contr.sum","contr.poly"))
ANCOVA_greens1_intxn <- aov(sqrt_BT_green_perc ~ sqrt_UPLC_chlb_perc * investigator, data=data_chlb_total)
Anova(ANCOVA_greens1_intxn, type="III")
### The category variable (investigator) is significant,
### so the intercepts among groups are different

# Compare the two models.
anova(ANCOVA_greens1_add,ANCOVA_greens1_intxn)
```

```{r, echo=FALSE}
greens2_covariates <- ggplot(data_chlb_total,
 aes(y=sqrt_BT_green,x=sqrt_UPLC_chlb, color=investigator)) +
 geom_point(size=3, alpha = 0.6,  position = position_jitter())+
 geom_smooth(method = "lm", se=FALSE) +
 ggtitle("Green algae")+
 expand_limits(y=0.8,x=0.2)+
 scale_y_continuous(breaks=pretty_breaks(n=5), name = expression(sqrt~greens["BT"]~(mu*g/cm^2))) +
 scale_x_continuous(breaks=pretty_breaks(n=5), name = expression(sqrt~chlb["UPLC"]~(mu*g/cm^2))) +
    scale_color_manual(values=investigator_colors,
                    name="Site",
                    breaks=c("Chris","Bella","Whit","Tristan"),
                    labels=c("SRL", "LV", "PR", "RMNP"))+
  theme(legend.position="none")
  greens2_covariates


```

```{r, tidy=TRUE, collapse=TRUE}
ANCOVA_greens2_add <- lm(sqrt_BT_green ~ sqrt_UPLC_chlb + investigator, data=data_chlb_total)

library(car)
options(contrasts=c("contr.sum","contr.poly"))
ANCOVA_greens2_intxn <- aov(sqrt_BT_green ~ sqrt_UPLC_chlb * investigator, data=data_chlb_total)
Anova(ANCOVA_greens2_intxn, type="III")
anova(ANCOVA_greens2_add,ANCOVA_greens2_intxn)
### The category variable (investigator) is significant,
### so the intercepts among groups are different
```

#####Mixed effect model greens + investigator (proxy for site)
Relative abundances
```{r mixed effect model greens, tidy=TRUE, collapse=TRUE}
library(lme4)
library(lmerTest)##Provides a p-value for the model but package needs to be unattached if you're using lsmeans to look at differences among a factor. For some reason lsmeans won't work with this package. 
library(MuMIn)

Fit1_chlb=lmer(sqrt_BT_green_perc~sqrt_UPLC_chlb_perc +(1+sqrt_UPLC_chlb_perc|investigator), data=data_chlb_total)
##Specifying different intercepts for investigators via the "1+" and different slopes for investigators by putting x in front of Investigator. 
plot(Fit1_chlb)
qqPlot(residuals(Fit1_chlb))
Fit1_chlb
summary(Fit1_chlb)
r.squaredGLMM(Fit1_chlb)
##Note: this provides a marginal R2m and conditional R2c. Marginal R2 quantifies only the variance explained by the fixed factor, while conditional R2 quantifies variance explained by fixed and random factors. 
```

Pigment concentrations
```{r}
Fit2_chlb=lmer(sqrt_BT_green~sqrt_UPLC_chlb +(1+sqrt_UPLC_chlb|investigator), data=data_chlb_total) ##Specifying different intercepts for investigators via the "1+" and different slopes for investigators by putting x in front of Investigator. 
plot(Fit2_chlb)
qqPlot(residuals(Fit2_chlb))
Fit2_chlb
summary(Fit2_chlb)
r.squaredGLMM(Fit2_chlb) ##Note: this provides a marginal R2m and conditional R2c. Marginal R2 quantifies only the variance explained by the fixed factor, while conditional R2 quantifies variance explained by fixed and random factors. 
```

##Diatoms
#####ANCOVA diatoms + investigator (proxy for site)
Relative abundances
```{r, echo=FALSE, fig.width=8}
diatoms1_covariates <- ggplot(data_fuco, aes(y=log_BT_diat_perc,x=log_UPLC_diat_perc, color=investigator)) +
  geom_point(size=3, alpha = 0.6,  position = position_jitter())+
  geom_smooth(method = "lm", se=FALSE) +
  ggtitle("Diatoms")+
  expand_limits(y=0.3,x=0.3)+
  scale_y_continuous(breaks=pretty_breaks(), name = expression("log"~rel.~abund.~diatoms["BT"]~"")) +
  scale_x_continuous(breaks=pretty_breaks(), name = expression("log"~rel.~abund.~fuco["UPLC"]~"")) +
  scale_color_manual(values=investigator_colors,
                    name="Site",
                    breaks=c("Chris","Bella","Whit","Tristan"),
                    labels=c("SRL", "LV", "PR", "RMNP"))+
    theme(legend.position="none")
diatoms1_covariates

# diatoms1_covariates_corrected <- ggplot(data_fuco, aes(y=log_BT_diat_perc2,x=log_UPLC_diat_perc2, color=investigator)) +
#   geom_point(size=3, alpha = 0.6,  position = position_jitter())+
#   geom_smooth(method = "lm", se=FALSE) +
#   ggtitle("Diatoms - corrected")+
#   expand_limits(y=0.3,x=0.3)+
#   scale_y_continuous(breaks=pretty_breaks(n=5), labels= scales::percent,  name = expression(log~diatoms["BT"]~"%")) +
#   scale_x_continuous(breaks=pretty_breaks(n=4), labels= scales::percent,  name = expression(log~fuco["UPLC"]~"%")) +
#   scale_color_manual(values=investigator_colors,
#                     name="Site",
#                     breaks=c("Chris","Bella","Whit","Tristan"),
#                     labels=c("SRL", "LV", "PR", "RMNP"))+
#     theme(legend.position="none")
# diatoms1_covariates_corrected
# 
# diatoms1_covariates_untransformed <- ggplot(data_fuco, aes(y=bentho_diatom_percent,x=perc_diat_UPLC, color=investigator)) +
#   geom_point(size=3, alpha = 0.6,  position = position_jitter())+
#   geom_smooth(method = "lm", se=FALSE) +
#   ggtitle("Diatoms - untransformed")+
#   expand_limits(y=0.3,x=0.3)+
#   scale_y_continuous(breaks=pretty_breaks(n=5), labels= scales::percent,  name = expression(diatoms["BT"]~"%")) +
#   scale_x_continuous(breaks=pretty_breaks(n=4), labels= scales::percent,  name = expression(fuco["UPLC"]~"%")) +
#   scale_color_manual(values=investigator_colors,
#                     name="Site",
#                     breaks=c("Chris","Bella","Whit","Tristan"),
#                     labels=c("SRL", "LV", "PR", "RMNP"))+
#     theme(legend.position="none")
# diatoms1_covariates_untransformed
```

Relative abundances
```{r ANCOVA diatoms, tidy=TRUE, collapse=TRUE}
library(car)
ANCOVA_diatoms1_add <- lm(log_BT_diat_perc ~ log_UPLC_diat_perc + investigator, data=data_fuco)
Anova(ANCOVA_diatoms1_add)

options(contrasts=c("contr.sum","contr.poly"))
ANCOVA_diatoms1_intxn <- aov(log_BT_diat_perc ~ log_UPLC_diat_perc * investigator, data=data_fuco)
Anova(ANCOVA_diatoms1_intxn, type="III")
### The category variable (investigator) is significant,
### so the intercepts among groups are different

# Compare the two models.
anova(ANCOVA_diatoms1_add,ANCOVA_diatoms1_intxn)
```

Pigment concentrations
```{r, echo=FALSE}
diatoms2_covariates <- ggplot(data_fuco, aes(y=log_BT_diat,x=log_UPLC_diat, color=investigator)) +
  geom_point(size=3, alpha = 0.6,  position = position_jitter())+
  geom_smooth(method = "lm", se=FALSE) +
  ggtitle("Diatoms")+
  expand_limits(y=0.8,x=0.2)+
  scale_y_continuous(breaks=pretty_breaks(n=5), name = expression(log~diatoms["BT"]~(mu*g/cm^2))) +
  scale_x_continuous(breaks=pretty_breaks(n=5), name = expression(log~fuco["UPLC"]~(mu*g/cm^2))) +
  scale_color_manual(values=investigator_colors,
                    name="Sample site",
                    breaks=c("Chris","Bella","Whit","Tristan"),
                    labels=c("SRL", "LV", "PR", "RMNP"))+
    theme(legend.position="none")
diatoms2_covariates


```

Pigment concentrations
```{r,tidy=TRUE, collapse=TRUE}
ANCOVA_diatoms2_add <- lm(log_BT_diat ~ log_UPLC_diat + investigator, data=data_fuco)

library(car)
options(contrasts=c("contr.sum","contr.poly"))
ANCOVA_diatoms2_intxn <- aov(log_BT_diat ~ log_UPLC_diat * investigator, data=data_fuco)
Anova(ANCOVA_diatoms2_intxn, type="III")
anova(ANCOVA_diatoms2_add,ANCOVA_diatoms2_intxn)
### The category variable (investigator) is significant,
### so the intercepts among groups are different
```

#####Mixed effect model diatoms + investigator (proxy for site)
Pigment concentrations
```{r,tidy=TRUE, collapse=TRUE}
library(lme4)
library(lmerTest) ##Provides a p-value for the model but package needs to be unattached if you're using lsmeans to look at differences among a factor. For some reason lsmeans won't work with this package. 
library(MuMIn)

Fit1_fuco=lmer(log_BT_diat~log_UPLC_diat +(1+log_UPLC_diat|investigator), data=data_fuco) ##Specifying different intercepts for investigators via the "1+" and different slopes for investigators by putting x in front of Investigator. 
par(mfrow=c(1,1))
plot(Fit1_fuco)
qqPlot(residuals(Fit1_fuco))
summary(Fit1_fuco)
r.squaredGLMM(Fit1_fuco) ##Note: this provides a marginal R2m and conditional R2c. Marginal R2 quantifies only the variance explained by the fixed factor, while conditional R2 quantifies variance explained by fixed and random factors. 
```

Relative abundances
```{r, tidy=TRUE, collapse=TRUE}
Fit2_fuco=lmer(log_BT_diat_perc~log_UPLC_diat_perc +(1+log_UPLC_diat_perc|investigator), data=data_fuco) ##Specifying different intercepts for investigators via the "1+" and different slopes for investigators by putting x in front of Investigator. 
par(mfrow=c(1,1))
plot(Fit2_fuco)
qqPlot(residuals(Fit2_fuco))
summary(Fit2_fuco)
r.squaredGLMM(Fit2_fuco) ##Note: this provides a marginal R2m and conditional R2c. Marginal R2 quantifies only the variance explained by the fixed factor, while conditional R2 quantifies variance explained by fixed and random factors. 
```


##Cyano
#####ANCOVA cyano + investigator (proxy for site)
Relative abundances
```{r, echo=FALSE}
cyano1_covariates <- ggplot(data_myxo_full, aes(y=sqrt_BT_cyano_perc,x=sqrt_UPLC_myxo_perc, color=investigator)) +
  geom_point(size=3, alpha = 0.6,  position = position_jitter())+
   geom_smooth(method = "lm", se=FALSE) +
  ggtitle("Cyanobacteria")+
  expand_limits(y=1.0,x=0.4)+
  scale_y_continuous(breaks=pretty_breaks(), name = expression("sqrt"~rel.~abund.~cyano["BT"]~"")) +
  scale_x_continuous(breaks=pretty_breaks(), name = expression("sqrt"~rel.~abund.~myxo["UPLC"]~"")) +
  scale_color_manual(values=investigator_colors,
                    name="Sample site",
                    breaks=c("Chris","Bella","Whit","Tristan"),
                    labels=c("SRL", "LV", "PR", "RMNP"))+
    theme(legend.position="none")
cyano1_covariates


```

Relative abundances
```{r ANCOVA cyano,tidy=TRUE, collapse=TRUE}
library(car)
ANCOVA_cyano1_add <- lm(sqrt_BT_cyano_perc ~ sqrt_UPLC_myxo_perc + investigator, data=data_myxo_full)
Anova(ANCOVA_cyano1_add)

options(contrasts=c("contr.sum","contr.poly"))
ANCOVA_cyano1_intxn <- aov(sqrt_BT_cyano_perc ~ sqrt_UPLC_myxo_perc * investigator, data=data_myxo_full)
Anova(ANCOVA_cyano1_intxn, type="III")
### The category variable (investigator) is significant,
### so the intercepts among groups are different

# Compare the two models.
anova(ANCOVA_cyano1_add,ANCOVA_cyano1_intxn)
```

Pigment concentrations
```{r, echo=FALSE}
cyano2_covariates <- ggplot(data_myxo_full, aes(y=sqrt_BT_cyano,x=sqrt_UPLC_myxo, color=investigator)) +
  geom_point(size=3, alpha = 0.6,  position = position_jitter())+
  geom_smooth(method = "lm", se=FALSE) +
  ggtitle("Cyanobacteria")+
    expand_limits(y=0.8,x=0.2)+
  scale_y_continuous(breaks=pretty_breaks(n=5),name = expression(sqrt~cyano["BT"]~(mu*g/cm^2))) +
  scale_x_continuous(breaks=pretty_breaks(n=5),name = expression(sqrt~myxo["UPLC"]~(mu*g/cm^2))) +
  scale_color_manual(values=investigator_colors,
                    name="Sample site",
                    breaks=c("Chris","Bella","Whit","Tristan"),
                    labels=c("SRL", "LV", "PR", "RMNP"))+
    theme(legend.position="none")
cyano2_covariates



```

Pigment concentrations
```{r,tidy=TRUE, collapse=TRUE}
ANCOVA_cyano2_add <- lm(sqrt_BT_cyano ~ sqrt_UPLC_myxo + investigator, data=data_myxo_full)

library(car)
options(contrasts=c("contr.sum","contr.poly"))
ANCOVA_cyano2_intxn <- aov(sqrt_BT_cyano ~ sqrt_UPLC_myxo * investigator, data=data_myxo_full)
Anova(ANCOVA_cyano2_intxn, type="III")
anova(ANCOVA_cyano2_add,ANCOVA_cyano2_intxn)
### The category variable (investigator) is significant,
### so the intercepts among groups are different
```

#####Mixed effect model cyano + investigator (proxy for site)
Relative abundances
```{r mixed effect model cyano,tidy=TRUE, collapse=TRUE}
library(lme4)
library(lmerTest) ##Provides a p-value for the model but package needs to be unattached if you're using lsmeans to look at differences among a factor. For some reason lsmeans won't work with this package. 
library(MuMIn)

Fit1_myxo=lmer(sqrt_BT_cyano_perc~sqrt_UPLC_myxo_perc +(1+sqrt_UPLC_myxo_perc|investigator), data=data_myxo_full) ##Specifying different intercepts for investigators via the "1+" and different slopes for investigators by putting x in front of Investigator. 
plot(Fit1_myxo)
qqPlot(residuals(Fit1_myxo))
summary(Fit1_myxo)
r.squaredGLMM(Fit1_myxo) ##Note: this provides a marginal R2m and conditional R2c. Marginal R2 quantifies only the variance explained by the fixed factor, while conditional R2 quantifies variance explained by fixed and random factors. 
```

Pigment concentrations
```{r, tidy=TRUE, collapse=TRUE}
Fit2_myxo=lmer(sqrt_BT_cyano~sqrt_UPLC_myxo +(1+sqrt_UPLC_myxo|investigator), data=data_myxo_full) ##Specifying different intercepts for investigators via the "1+" and different slopes for investigators by putting x in front of Investigator. 
plot(Fit2_myxo)
qqPlot(residuals(Fit2_myxo))
summary(Fit2_myxo)
r.squaredGLMM(Fit2_myxo) ##Note: this provides a marginal R2m and conditional R2c. Marginal R2 quantifies only the variance explained by the fixed factor, while conditional R2 quantifies variance explained by fixed and random factors. 
```



##Total chl
#####ANCOVA chla + investigator
```{r ANCOVA chla, echo=FALSE}
chla_investigator <- ggplot(data_chla_total, aes(y=log_BT_chla,x=log_UPLC_chla, color=investigator)) +
  geom_point(size=3, alpha = 0.6,  position = position_jitter())+
  geom_smooth(method = "lm", se=FALSE) +
  ggtitle(expression(paste(bold("Total chlorophyll "), bolditalic("a"))))+
  expand_limits(x=1.0, y=1.0)+
  scale_y_continuous(breaks=pretty_breaks(n=5), name = expression(log~Chl~italic("a")["BT"]~(mu*g/cm^2))) +
  scale_x_continuous(breaks=pretty_breaks(n=5), name = expression(log~Chl~italic("a")["UPLC"]~(mu*g/cm^2))) +
  scale_color_manual(values=investigator_colors,
                    name="Sample site",
                    breaks=c("Chris","Bella","Whit","Tristan"),
                    labels=c("SRL", "LV", "PR", "RMNP")) +
  theme(legend.position="right")
chla_investigator



```

```{r,tidy=TRUE, collapse=TRUE}
ANCOVA_chla1_add <- lm(log_BT_chla ~ log_UPLC_chla + investigator, data=data_chla_total)
anova(ANCOVA_chla1_add)
summary(ANCOVA_chla1_add)
Anova(ANCOVA_chla1_add)

library(car)
options(contrasts=c("contr.sum","contr.poly"))
ANCOVA_chla1_intxn <- aov(log_BT_chla ~ log_UPLC_chla * investigator, data=data_chla_total)
Anova(ANCOVA_chla1_intxn, type="III")
### The category variable (investigator) is significant,
### so the intercepts among groups are different

# Compare the two models.
anova(ANCOVA_chla1_add,ANCOVA_chla1_intxn)
```

#####Mixed effect model chla + investigator 
```{r mixed effect model diatoms,tidy=TRUE, collapse=TRUE}
library(lme4)
library(lmerTest) ##Provides a p-value for the model but package needs to be unattached if you're using lsmeans to look at differences among a factor. For some reason lsmeans won't work with this package. 
library(MuMIn)

Fit1_chla=lmer(log_BT_chla~log_UPLC_chla +(1+log_UPLC_chla|investigator), data=data_chla_total) ##Specifying different intercepts for investigators via the "1+" and different slopes for investigators by putting x in front of Investigator. 
plot(Fit1_chla)
qqPlot(residuals(Fit1_chla))

summary(Fit1_chla)
r.squaredGLMM(Fit1_chla) ##Note: this provides a marginal R2m and conditional R2c. Marginal R2 quantifies only the variance explained by the fixed factor, while conditional R2 quantifies variance explained by fixed and random factors. 
```

#ANCOVA combined plot
```{r, echo=FALSE, tidy=TRUE}
library(grid) 
library(ggpubr)
library(gridExtra)


###UPDATED STACKED FIGURE FOR MANUSCRIPT (Figure 2)
chla_panel_ancova <- ggarrange(NULL,chla_investigator,NULL,
                        ncol=3,nrow=1,
                        widths=c(0.2,0.8,0.2),
                        labels=c("","A",""),
                        legend=NULL)
all_stacked_ancova <- ggarrange(chla_panel_ancova,
               ggarrange(
                        greens1_covariates, greens2_covariates,
                        diatoms1_covariates, diatoms2_covariates,
                        cyano1_covariates , cyano2_covariates ,
          align="hv",
          ncol = 2, nrow = 3,
          labels = c("B", "C", "D", "E", "F", "G")),
          nrow=2,
          widths = c(4,4), heights = c(0.3,1.0))
ggsave("figures/ANCOVA_combined_12x16_transformation_fixed.tiff", width=12, height=16,units="in")
ggsave("figures/ANCOVA_combined_10x16_transformation_fixed.tiff", width=10, height=16,units="in")




```